A large and variable leading tail of Helium in a sub-Saturn undergoing runaway inflation

### 2023-06-21 paper/paper1/ms.tex
Confirm consistency of figure and Temperature label, flagged by Morgan

But inflated hot Saturns are rare \citep{2018AJ....155..214T}.  The cause for their underabundance remains an open question, with two leading candidate explanations.  Tidal migration mechanisms may be mass-dependent in such a way as to proceed efficiently for Jupiter-mass planets, but inefficiently for the lower-mass Saturns.  In this scenario, sub-Saturn mass planets never make it to the close-in orbital separations that would lead to the conditions needed for inflation in the first place.

@@

Equipped with these two SEDs of differing radiation hardness, we explored different mass loss rates and exosphere temperatures.  Figure \ref{fig:pwinds} shows one example model spectrum with $\dot{M} = 2\times 10^{13}$ g/s, and $T_0=14000$~K, with an XUV spectrum possessing $L_x/L_\mathrm{bol}=10^{-5}$.  This mass loss rate would imply a characteristic lifetime of $\sim$2000 Myr.  The model spectrum exhibits approximately the same equivalent width as our HPF observations, making it a hypothetical scenario among a family of partially degnerate solutions.

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figures/pwinds_May2020_14000_2e13Mdot_medXUV_formal_rv copy.png}
    \caption{Simulated 1D Parker wind model of Helium absorption in \hatpb.  The spectrum was generated with a mass loss rate of $2\times10^{13}$ g/s, exosphere gas temperature of 14000 K, and with an XUV luminosity $L_x/L_\mathrm{bol}=10^{-5}$ intermediate between those shown in Figure \ref{fig:XUV}.  The \texttt{p-winds} model yields the \ion{He}{1} 10830 triplet lines (colored dashed lines), with a cumulative feature in black resembling the data, shown as the May 2020 in-transit mean.  Additional 3D velocity dispersion of the gas can explain differences between the line shapes of the model and data.  Overall the 1D models may be too simplistic to represent the inherently 3D structure of the outflow.}
    \label{fig:pwinds}
\end{figure}

>>>>

But inflated hot Saturns are rare \citep{2018AJ....155..214T}.  The cause for their underabundance remains an open question, with two leading candidate explanations.  Tidal migration mechanisms may be mass-dependent in such a way as to proceed efficiently for Jupiter-mass planets, but inefficiently for the lower-mass Saturns \citep{2018AJ....155..214T,2018ARA&A..56..175D}.  In this scenario, sub-Saturn mass planets never make it to the close-in orbital separations that would lead to the conditions needed for inflation in the first place.

@@

Equipped with these two SEDs of differing radiation hardness, we explored different mass loss rates and exosphere temperatures.  Figure \ref{fig:pwinds} shows one example model spectrum with $\dot{M} = 2\times 10^{13}$ g/s, and $T_0=14\,000$~K, with an XUV spectrum possessing $L_x/L_\mathrm{bol}=10^{-5}$.  This mass loss rate would imply a characteristic lifetime of $\sim$1000 Myr.  The model spectrum exhibits approximately the same equivalent width as our HPF observations, making it a hypothetical scenario among a family of partially degnerate solutions.

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figures/pwinds_May2020_14000_2e13Mdot_medXUV_formal_rv copy.png}
    \caption{Simulated 1D Parker wind model of Helium absorption in \hatpb.  The spectrum was generated with a mass loss rate of $2\times10^{13}$ g/s, exosphere gas temperature of $14\,000\;$K, and with an XUV luminosity $L_x/L_\mathrm{bol}=10^{-5}$ intermediate between those shown in Figure \ref{fig:XUV}.  The \texttt{p-winds} model yields the \ion{He}{1} 10830 triplet lines (colored dashed lines), with a cumulative feature in black resembling the data, shown as the May 2020 in-transit mean.  Additional 3D velocity dispersion of the gas can explain differences between the line shapes of the model and data.  Overall the 1D models may be too simplistic to represent the inherently 3D structure of the outflow.}
    \label{fig:pwinds}
\end{figure}
